Lineage Analysis of CRISPR and shRNA Screens

### 2018-08-20 lineages_18Q3.Rmd

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./../data_munging/danielc_cell_line_database_completed_extra_SE.tsv", sep = "\t", row.names = NULL, header = TRUE)
colnames(ccl_converter)[4] <- "CCLE_Name"
colnames(ccl_converter)[10] <- "Broad_ID"
```

@@

saveRDS(ge_melt, "./data_munging/rds/ge_melt_18Q3.rds", compress = "xz")
```

```{r}
ge_melt <- readRDS("./data_munging/rds/ge_melt_18Q3.rds")
```

@@

The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
```{r, eval=TRUE}
crispr <- read.delim("././data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(crispr) <- gsub(" .*", "", colnames(crispr))
```

@@

saveRDS(shrna_data, "./data_munging/rds/shrna_data_18Q3.rds", compress = "xz")
```

```{r}
shrna_data <- readRDS("./data_munging/rds/shrna_data_18Q3.rds")
shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
```

```{r, eval=FALSE}
write(union(as.character(distinct(crispr_data[which(is.na(crispr_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name), as.character(distinct(shrna_data[which(is.na(shrna_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name)), file = "./../../../Desktop/na_ccl_in_converter.txt")
```

@@

```{r, eval=FALSE}
shrna_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
shrna_signif_lineage <- adj_signif(shrna_signif_lineage)
shrna_signif_lineage <- mutate(shrna_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
saveRDS(shrna_signif_lineage, "./data_munging/rds/shrna_signif_lineage.rds")
```

```{r, eval=FALSE}
shrna_signif_lineage <- readRDS("./data_munging/rds/shrna_signif_lineage.rds")
```

>>>>

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/danielc_cell_line_database_completed_extra_SE.tsv", sep = "\t", row.names = NULL, header = TRUE)
colnames(ccl_converter)[4] <- "CCLE_Name"
colnames(ccl_converter)[10] <- "Broad_ID"
```

@@

saveRDS(ge_melt, "./../ge_melt_18Q3.rds", compress = "xz")
```

```{r}
ge_melt <- readRDS("./../ge_melt_18Q3.rds")
```

@@

The latest CRISPR CERES score data (18Q3, August 2018) was pulled from the [DepMap Data Portal](https://depmap.org/portal/download/) (Broad Institute Cancer Dependency Map 2018, Meyers et al. 2017).
```{r, eval=TRUE}
crispr <- read.delim("./data_munging/gene_effect_18Q3.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(crispr) <- gsub(" .*", "", colnames(crispr))
```

@@

saveRDS(shrna_data, "./../shrna_data_18Q3.rds", compress = "xz")
```

```{r}
shrna_data <- readRDS("./../shrna_data_18Q3.rds")
shrna_ccl <- data.frame("Broad_ID" = shrna_data$Broad_ID)
```

```{r, eval=FALSE}
write(union(as.character(distinct(crispr_data[which(is.na(crispr_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name), as.character(distinct(shrna_data[which(is.na(shrna_data$lineage_name)), c("CCLE_Name", "lineage_name")])$CCLE_Name)), file = "./data_munging//na_ccl_in_converter.txt")
```

@@

```{r, eval=FALSE}
shrna_signif_lineage <- compare_means(Score ~ Mutation_Status, group.by = c("Hugo_Symbol", "lineage_name"), data = shrna_data, method = "wilcox.test", p.adjust.method = "BH")
shrna_signif_lineage <- adj_signif(shrna_signif_lineage)
shrna_signif_lineage <- mutate(shrna_signif_lineage, lineage_name = reorder(lineage_name, p.adj, mean))
saveRDS(shrna_signif_lineage, "./../shrna_signif_lineage.rds")
```

```{r, eval=FALSE}
shrna_signif_lineage <- readRDS("./../shrna_signif_lineage.rds")
```
